The role of advection versus diffusion in intraventricular transport

### 2025-02-04 paper/main.tex
clean plot scripts, add seaborn dependency

% Title
\title{The role of advection versus diffusion in intraventricular transport}
\author[1,*]{Halvor Herlyng}
\author[1]{Ada J.~Ellingsrud}
\author[1]{Miroslav Kuchta} 
\author[\fixme{X}]{Inyoung Jeong} % OK?
\author[1,3,+]{Marie E.~Rognes} % OK order?
\author[2,+, *]{Nathalie Jurisch-Yaksi}
\affil[1]{Department of Numerical Analysis and Scientific Computing,
Simula Research Laboratory, Oslo, Norway}
\affil[2]{\fixme{@Nathalie is this correct?: Department of Clinical and Molecular Medicine,
Norwegian University of Science and Technology, Trondheim, Norway \\
Same affiliation for Inyoung?}}
\affil[3]{K.~G.~Jebsen Center for Brain Fluid Research}
\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no}
\href{mailto:nathalie.jurisch-yaksi@ntnu.no}{nathalie.jurisch-yaksi@ntnu.no}}
\affil[+]{these authors contributed equally to this work}
% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={zebrafish-cilia-csf},
  pdfauthor={H.~Herlyng~\emph{et al.}}
}
\fi

@@

To date, it remains poorly understood how cilia contribute to the overall fluid
flow and solute transport in the brain.
These questions have been especially challenging to tackle due to technical limitations.
Notably, cilia are very small and beat at high frequencies ranging from 10 to 30 Hz,
while other fluid dynamic processes in the brain are slower and span larger three-dimensional volumes.
Most studies until now have analyzed one process at a time, especially in mammals.
For instance, multiple studies have convincingly shown that cilia generate complex
flow patterns at the surface of the brain ventricles.
However, since all these studies have been performed on brain explants, they failed
to identify the role of pressure gradients associated with respiration and heart pulsations in CSF transport.
Similarly, while MRI technology can measure CSF movement in humans, it cannot detect
the fast movements of cilia or understand their impact in the large human brain.
Consequently, we lack a comprehensive understanding of how cilia contribute to CSF
movement and solute transport, and whether cilia dysfunction will alter CSF distribution
and lead to brain disorders.
This is particularly important since ventricular enlargement or hydrocephalus is
commonly observed in animal models with motile cilia deficiency, potentially affecting
brain activity and behavior.

@@

\section*{Methods}
\subsection*{Image-based computational geometries of zebrafish brain ventricles}
To model flow and transport in zebrafish larval brain ventricles, we generated a
3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
From the imaging data, we constructed a computational mesh of the ventricles (\Cref{fig:fig1}\fixme{d}).
The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a
maximal (minimal) edge length of 14.9 $\mu$m (4.68 $\mu$m). 
At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts. 
Parts of the ventricular surfaces were marked to be lined with
motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:fig1}\fixme{d}, magenta markers).
\begin{figure}%[hbt!]
    \centering
    \includegraphics[width=\linewidth]{graphics/figure1.png}
    \caption{\fixme{Reorder panels.} 
    \textbf{a.} Schematic illustration of the two cerebrospinal fluid (CSF) flow components modeled,
    motile cilia and cardiac pulsations, and their contributions to the flow patterns.
    \textbf{b.} Particle tracking data visualizing flow directionality in the middle ventricle.
    \textbf{c.} Flow velocity magnitudes in the middle ventricle from particle tracking data.
    \textbf{d.} Computational mesh with marked facets indicating regions of motile cilia (magenta) and
    anterior/posterior facets (blue).
    \textbf{e.} Streamlines of the (steady-state) CSF flow field simulated with the
    cilia-only/no-cardiac flow model.
    \textbf{f.} Streamlines of the CSF flow field simulated with the cardiac-only/no-cilia flow
    model at a time 25\% into the cardiac cycle. %t=0.112613 s, period=0.45045 s
    \textbf{g.} Streamlines simulated with the baseline flow model at
    a time 50\% into the cardiac cycle. %t=0.225225 s
    \textbf{h.} Streamlines simulated with the baseline flow model at
    a time 70\% into the cardiac cycle. %t=0.315315 s
    }
    \label{fig:fig1}
\end{figure}

@@

The larval and adult zebrafish were raised under standard husbandry
conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
The fish tanks were kept at constant pH 7.0 and 685 $\mu$S with a
14/10 hr light/dark cycle.
From fertilization to 3 dpf, larvae were maintained in egg
water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
and subsequently transferred to artificial fish water (AFW)
(1.2 g marine salt in 20 L RO water). The zebrafish lines used in the experiments were
\emph{ccdc103(dnaaf19)\textsuperscript{tn222a}}
(\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}
and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures},
\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}
(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.

@@

\subsection*{Genotyping of adult zebrafish}
Genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult
fish using 100 $\mu$L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA,
tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
To stop the lysis reaction, the samples were heated to 95°C for 10 minutes
and then centrifuged at 13000 rpm for 2 minutes.
The supernatant containing gDNA was utilized for KASP assays-based analysis.
The gDNAs were diluted (1:2) with water, and 3 $\mu$L of the diluted gDNA was
used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
For each sample well, the master mix contained: 5 $\mu$L of master mix; 0.14
$\mu$L of assay mix; 1.86 $\mu$L of RO water.

@@

For photoconversion, ‘Bleaching’ and ‘Region’ in the ZEN software
were used. A 405 nm laser was focused into a circular area (diameter: 16 $\mu$m, scan 0.77 $\mu$sec/pixel)
of the dorsoposterior diencephalic ventricle with 100\% laser power.
The laser was illuminated in the area repeatedly between each scanning.
After imaging, the fish health was checked and only data from healthy fish were analyzed.
Data were collected and analyzed from three separate experiments,
with a total of 8 controls and 6 mutants.

@@

Following injection, the zebrafish was directly placed under the confocal
microscope and 1200 images were acquired at a frequency of 13.1 Hz.
A single optical section was obtained. Particle tracking was done using
TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis}
and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
The parameters for TrackMate were as follows.
The DoG detector was used with the settings: threshold: 2.0, with
median filtering; radius: 2.0, with subpixel localization.
Next, the Simple LAP tracker was used with settings: max frame gap: 2;
alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0;
splitting max distance: 15.0; allow gap closing: true; allow track splitting:
false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
Only the particle tracks with at least 30 data points, while simultaneously
covering a distance of at least 8.8 $\mu$m, were plotted in~\Cref{fig:fig1}\fixme{b, c}.

@@

\subsection*{Absence of ciliary motion affects local protein distribution}
Since CSF flow is highly disturbed in the absence of motile cilia, we
want to assess the impact of cilia motion on solute distribution. To this end,
we measured the movement of photoconverted Dendra2 signal
in control and motile-cilia mutant zebrafish (\emph{schmalhans} (\emph{smh})).
By plotting the means of $\Delta F$ (\Cref{fig:figure4_compare_control_mutant}a)
and the time to threshold
across the control and mutant cohorts (\Cref{fig:figure4_compare_control_mutant}b),
we identified a significant
difference in Dendra2 distribution in ROIs 2 and 4, but not in ROIs 3, 5, and 6. In ROIs 2 and 4,
which measure Dendra2 distribution downstream of the photoconversion site,
we observed a slower increase of fluorescence intensity,
resulting in $\sim 45\%$ (ROI 2) and \fixme{$\sim X\%$ (ROI 4)}
higher mean times-to-threshold in the \emph{smh}
mutants compared to controls (\Cref{fig:figure4_compare_control_mutant}b).

@@

We identified that the velocities were most strongly
affected when removing cilia in the dorsal diencephalic cilia,
as the maximum velocity dropped from 27.7 $\mu$m/s to 8.0 $\mu$m/s.
\emph{In vivo}, these cilia generate the strongest flow at
this developmental stage of the fish~\cite{Olstad2019CiliaryDevelopment}.
In contrast, removing telencephalic and ventral diencephalic had minimal
impact and resulted in maximum velocities of 27.7 $\mu$m/s or 27.2 $\mu$m/s, respectively.
Changes in the transport dynamics of Dendra2 were most prominent when removing the dorsal cilia
in the diencephalic ventricle. All ROIs (except ROI 1, where we impose the photoconversion curve)
exhibit significant changes in the dynamics of $\cbar$
(\Cref{fig:figure5_compare_cilia_modifications}b).
Compared to the baseline model results, we observed a slower increase and lower final concentration
in the middle and anterior ventricles (ROIs 2--5),
and more rapid transport to the posterior ventricle (ROI 6).
On the other hand, removal of telencephalic cilia did not alter the evolution of the
mean concentration $\cbar$ with time (\Cref{fig:figure5_compare_cilia_modifications}b).
Finally, without ventral cilia in the diencephalic ventricle,
more solute has spread towards the anterior ventricle (ROI 5) and
less solute has spread towards the posterior ventricle (ROI 6).
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure5_compare_cilia_modifications.png}
    \caption{\textbf{a.} The three separate ciliated regions where loss of cilia motility is simulated
    by imposing a zero tangential traction boundary condition in the respective region.
    \textbf{b.} Mean concentration $\cbar(t)$ for the six regions of interest in the three 
    loss-of-cilia-motility scenarios considered. The region named in the legend is the region
    where we modify the cilia tangential traction boundary condition to a free-slip condition
    in the CSF flow model.}
    \label{fig:figure5_compare_cilia_modifications}
\end{figure}

@@

Meanwhile, we identified that transport of larger molecules
(thus with smaller diffusion coefficients),
such as 200 nm exosomes, are almost entirely dependent on advection.
Indeed, there was essentially zero solute in the posterior ventricle at the
final simulation time (around 850 s), where transport is largely driven by diffusion.
For $D_1$, an estimate of the diffusion timescale $t_d=L^2/D_1$ over a distance
$L=200$ $\mu$m from the middle to the posterior ventricle is approximately 24500 s.
Advective transport by the mean velocity $\overline{U}=1.41 \ \mu$m/s over the same distance would happen
on a timescale of the order of $t_a=L/\overline{U}=141$ s. Comparing this with the minuscule values of
$\cbar_6$ after simulating transport with $D_1$ for 850 s, one can conclude that if advection
played a role in transporting solute from the photoconversion site in the middle ventricle
to the posterior ventricle, values of $\cbar_6$ would be higher than those observed.

@@

\subsection*{Computational model assumptions and boundary conditions}
To model CSF, we employed slip boundary conditions at the ventricular walls,
contrasting the classical choice of a noslip boundary condition.
The use of slip boundary conditions is motivated by experimental observations of the
flow field in zebrafish embryo brain ventricles~\cite{Olstad2019CiliaryDevelopment}.
It has been observed, both previously and in this work, that the fluid velocity increases
towards the wall~(\Cref{fig:fig1}\fixme{c}).
Using slip boundary conditions allows for this behavior.
A couple of previous continuum model simulation studies of
cilia-mediated flow~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal}
have modeled cilia as body forces. We chose to model the cilia as a force exerted tangentially on the boundary.
First, we deem this a good representation of the real nature of cilia,
since they are in reality microscale structures confined to the ventricular walls that
generate flow through collective motion. Second, it avoids the need of excessive mesh
refinement near the ciliated boundaries in the case that a
body force were to be applied in a $\sim$ 5 $\mu$m~\cite{Salman2022ComputationalEmbryo} deep cilia layer.

@@

Particle movement varied over the different measurements. The mean of $\overline{u}_x$ was
0.26 $\mu$m/s and the mean of $\overline{u}_y$ was 0.08 $\mu$m/s. The maximum mean velocities
in absolute values were 10.2 $\mu$m/s and 2.4 $\mu$m/s for $\overline{u}_x$ and $\overline{u}_y$,
respectively. We used the only-cardiac/no-cilia flow model to tune the pressure boundary condition
amplitude $A$. The choice of $A=0.0015$ Pa was used since: (i) it yields a maximum velocity magnitude
of 4.8 $\mu$m/s, which is close to the maximum observed in the particle tracking data when
rejecting the outlier at around 10 $\mu$m/s; (ii) it yields a time-averaged mean velocity
of 0.89 $\mu$m/s, which is close to the mean observed in the particle tracking data.
\begin{figure}[H]
    \begin{minipage}[t]{0.49\textwidth}
        \includegraphics[width=\textwidth]{graphics/mean_velocities_x.png}
        \subcaption{Mean velocities in the $x$ direction of the particles tracked.}\label{fig:meanx}
    \end{minipage}
    \begin{minipage}[t]{0.49\textwidth}
        \includegraphics[width=\textwidth]{graphics/mean_velocities_y.png}
        \subcaption{Mean velocities in the $y$ direction of the particles tracked.}\label{fig:meany}
    \end{minipage} 
    \caption{Particle tracking data. The dashed horizontal line designates a value of zero.}\label{fig:particle_tracking_data}
\end{figure}
\clearpage
\bibliography{ref}{}
\end{document}

>>>>

% Title
\title{The role of advection versus diffusion in intraventricular transport}
\author[1,*]{Halvor Herlyng}
\author[1]{Ada J.~Ellingsrud}
\author[1]{Miroslav Kuchta} 
\author[FIX ME]{Inyoung Jeong} % OK?
\author[1,3,+]{Marie E.~Rognes} % OK order?
\author[2,+, *]{Nathalie Jurisch-Yaksi}
\affil[1]{Department of Numerical Analysis and Scientific Computing,
Simula Research Laboratory, Oslo, Norway}
\affil[2]{\fixme{@Nathalie is this correct?: Department of Clinical and Molecular Medicine,
Norwegian University of Science and Technology, Trondheim, Norway\\
Same affiliation for Inyoung?}}
\affil[3]{K.~G.~Jebsen Center for Brain Fluid Research}
\affil[*]{\href{mailto:hherlyng@simula.no}{hherlyng@simula.no}
\href{mailto:nathalie.jurisch-yaksi@ntnu.no}{nathalie.jurisch-yaksi@ntnu.no}}
\affil[+]{these authors contributed equally to this work}
% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={zebrafish-cilia-csf},
  pdfauthor={H.~Herlyng~\emph{et al.}}
}
\fi

@@

To date, it remains poorly understood how cilia contribute to the overall fluid
flow and solute transport in the brain.
These questions have been especially challenging to tackle due to technical limitations.
Notably, cilia are very small and beat at high frequencies ranging from 10 to 30 Hz,
while other fluid dynamic processes in the brain are slower and span larger volumes.
Most studies until now have analyzed one process at a time, especially in mammals.
For instance, multiple studies have convincingly shown that cilia generate complex
flow patterns at the surface of the brain ventricles.
However, since all these studies have been performed on brain explants, they failed
to identify the role of pressure gradients associated with respiration and heart pulsations in CSF transport.
Similarly, while MRI technology can measure CSF movement in humans, it cannot detect
the fast movements of cilia or understand their impact in the large human brain.
Consequently, we lack a comprehensive understanding of how cilia contribute to CSF
movement and solute transport, and whether cilia dysfunction will alter CSF distribution
and lead to brain disorders.
This is particularly important since ventricular enlargement or hydrocephalus is
commonly observed in animal models with motile cilia deficiency, potentially affecting
brain activity and behavior.

@@

\section*{Methods}
\subsection*{Image-based computational geometries of zebrafish brain ventricles}
To model flow and transport in zebrafish larval brain ventricles, we generated a
3D representation of the brain ventricular walls using confocal imaging data of a zebrafish embryo
injected intraventricularly with a 70 kDa dye at 2 dpf~\cite{Olstad2019CiliaryDevelopment}. 
From the imaging data, we constructed a computational mesh of the ventricles (\Cref{fig:fig1}\fixme{d}).
The interior volume was meshed with fTetWild~\cite{Hu2020FastWild}. 
The \emph{standard} mesh consisted of 132 134 tetrahedral cells and had a
maximal (minimal) edge length of 14.9 \textmu m (4.68 \textmu m). 
At 2 dpf, the ventricular system consists mainly of 3 cavities: the telencephalic (anterior),
the di-/mesencephalic (middle) and the rhombencephalic (posterior) ventricles, which are connected by ducts. 
Parts of the ventricular surfaces were marked to be lined with
motile cilia~\cite{Olstad2019CiliaryDevelopment} (\Cref{fig:fig1}\fixme{d}, magenta markers).
\begin{figure}%[hbt!]
    \centering
    \includegraphics[width=\linewidth]{graphics/figure1.png}
    \caption{\fixme{Reorder panels.} 
    \textbf{a.} Schematic illustration of the two cerebrospinal fluid (CSF) flow components modeled,
    motile cilia and cardiac pulsations, and their contributions to the flow patterns.
    \textbf{b.} Particle tracking data visualizing flow directionality in the middle ventricle.
    \textbf{c.} Flow velocity magnitudes in the middle ventricle from particle tracking data.
    \textbf{d.} Computational mesh with marked facets indicating regions of motile cilia (magenta) and
    anterior/posterior facets (blue).
    \textbf{e.} Streamlines of the (steady-state) CSF flow field simulated with the
    cilia-only/no-cardiac flow model.
    \textbf{f.} Streamlines of the CSF flow field simulated with the cardiac-only/no-cilia flow
    model at a time 25\% into the cardiac cycle. %t=0.112613 s, period=0.45045 s
    \textbf{g.} Streamlines simulated with the baseline flow model at
    a time 50\% into the cardiac cycle. %t=0.225225 s
    \textbf{h.} Streamlines simulated with the baseline flow model at
    a time 70\% into the cardiac cycle. %t=0.315315 s
    }
    \label{fig:fig1}
\end{figure}

@@

The larval and adult zebrafish were raised under standard husbandry
conditions at 28.5°C in a Techniplast Zebtech Multilinking system.
The fish tanks were kept at constant pH 7.0 and 685 \textmu S with a
14/10 hr light/dark cycle.
From fertilization to 3 dpf, larvae were maintained in egg
water (1.2 g marine salt and 0.1\% methylene blue in 20 L reverse osmosis (RO) water)
and subsequently transferred to artificial fish water (AFW)
(1.2 g marine salt in 20 L RO water). The zebrafish lines used in the experiments were
\emph{ccdc103(dnaaf19)\textsuperscript{tn222a}}
(\emph{schmalhans (smh)})~\cite{Jau-NianChen1997Left-rightZebrafish}
and \emph{Tg(gfap:Gal4FF)\textsuperscript{nw7Tg}}~\cite{DiazVerdugo2019Glia-neuronSeizures},
\emph{Tg(5xuas:Signal-Dendra2)\textsuperscript{nw21Tg}}.
Animals were in the pigmentless \emph{nacre\textsuperscript{b692}}
(\emph{mitfa\textsuperscript{-/-}})~\cite{JamesA.Lister1999NacreFate} background.

@@

\subsection*{Genotyping of adult zebrafish}
Genomic DNA (gDNA) was isolated from clipped fins of anesthetized adult
fish using 100 \textmu L of PCR lysis buffer (containing 1M tris pH 7--9, 0.5 M EDTA,
tritonX-100, and Proteinase K 0.1 mg/ml) overnight at 50°C.
To stop the lysis reaction, the samples were heated to 95°C for 10 minutes
and then centrifuged at 13000 rpm for 2 minutes.
The supernatant containing gDNA was utilized for KASP assays-based analysis.
The gDNAs were diluted (1:2) with water, and 3 \textmu L of the diluted gDNA was
used to perform the KASP assay following the guidelines of the manufacturer (LGC Biosearch Technologies™).
For each sample well, the master mix contained: 5 \textmu L of master mix; 0.14
\textmu L of assay mix; 1.86 \textmu L of RO water.

@@

For photoconversion, ‘Bleaching’ and ‘Region’ in the ZEN software
were used. A 405 nm laser was focused into a circular area (diameter: 16 \textmu m, scan 0.77 \textmu sec/pixel)
of the dorsoposterior diencephalic ventricle with 100\% laser power.
The laser was illuminated in the area repeatedly between each scanning.
After imaging, the fish health was checked and only data from healthy fish were analyzed.
Data were collected and analyzed from three separate experiments,
with a total of 8 controls and 6 mutants.

@@

Following injection, the zebrafish was directly placed under the confocal
microscope and 1200 images were acquired at a frequency of 13.1 Hz.
A single optical section was obtained. Particle tracking was done using
TrackMate~\cite{Tinevez2017TrackMate:Tracking} in Fiji/ImageJ~\cite{Schindelin2012Fiji:Analysis}
and plotted using MATLAB, as described in Jeong~\emph{et al.}~\cite{Jeong2022MeasurementTelencephalon}.
The parameters for TrackMate were as follows.
The DoG detector was used with the settings: threshold: 2.0, with
median filtering; radius: 2.0, with subpixel localization.
Next, the Simple LAP tracker was used with settings: max frame gap: 2;
alternative linking cost factor: 1.05; linking max distance: 5.0; gap closing max distance: 2.0;
splitting max distance: 15.0; allow gap closing: true; allow track splitting:
false; allow track merging: false; merging max distance: 15.0; cutoff percentile: 0.9.
Only the particle tracks with at least 30 data points, while simultaneously
covering a distance of at least 8.8 \textmu m, were plotted in~\Cref{fig:fig1}\fixme{b, c}.

@@

\subsection*{Absence of ciliary motion affects local protein distribution}
Since CSF flow is highly disturbed in the absence of motile cilia, we
want to assess the impact of cilia motion on solute distribution. To this end,
we measured the movement of photoconverted Dendra2 signal
in control and motile-cilia mutant zebrafish (\emph{schmalhans} (\emph{smh})).
By plotting the means of $\Delta F$ (\Cref{fig:figure4_compare_control_mutant}a)
and the time to threshold
across the control and mutant cohorts (\Cref{fig:figure4_compare_control_mutant}b),
we identified a significant
difference in Dendra2 distribution in ROIs 2 and 4, but not in ROIs 3, 5, and 6. In ROIs 2 and 4,
which measure Dendra2 distribution downstream of the photoconversion site,
we observed a slower increase of fluorescence intensity,
resulting in $\sim 45\%$ (ROI 2) and $\sim 25\%$ (ROI 4)
higher mean times-to-threshold in the \emph{smh}
mutants compared to controls (\Cref{fig:figure4_compare_control_mutant}b).

@@

We identified that the velocities were most strongly
affected when removing cilia in the dorsal diencephalic cilia,
as the maximum velocity dropped from 27.7 \textmu m/s to 8.0 \textmu m/s.
\emph{In vivo}, these cilia generate the strongest flow at
this developmental stage of the fish~\cite{Olstad2019CiliaryDevelopment}.
In contrast, removing telencephalic and ventral diencephalic had minimal
impact and resulted in maximum velocities of 27.7 \textmu m/s or 27.2 \textmu m/s, respectively.
Changes in the transport dynamics of Dendra2 were most prominent when removing the dorsal cilia
in the diencephalic ventricle. All ROIs (except ROI 1, where we impose the photoconversion curve)
exhibit significant changes in the dynamics of $\cbar$
(\Cref{fig:figure5_compare_cilia_modifications}b).
Compared to the baseline model results, we observed a slower increase and lower final concentration
in the middle and anterior ventricles (ROIs 2--5),
and more rapid transport to the posterior ventricle (ROI 6).
On the other hand, removal of telencephalic cilia did not alter the evolution of the
mean concentration $\cbar$ with time (\Cref{fig:figure5_compare_cilia_modifications}b).
Finally, without ventral cilia in the diencephalic ventricle,
more solute has spread towards the anterior ventricle (ROI 5) and
less solute has spread towards the posterior ventricle (ROI 6).
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure5_compare_cilia_modifications.png}
    \caption{\textbf{a.} The three separate ciliated regions where loss of cilia motility is simulated
    by imposing a zero tangential traction boundary condition in the respective region.
    \textbf{b.} Mean concentration $\cbar(t)$ for the six regions of interest in the three 
    loss-of-cilia-motility scenarios considered. The region named in the legend is the region
    where we modify the cilia tangential traction boundary condition to a free-slip condition
    in the CSF flow model.}
    \label{fig:figure5_compare_cilia_modifications}
\end{figure}

@@

Meanwhile, we identified that transport of larger molecules
(thus with smaller diffusion coefficients),
such as 200 nm exosomes, are almost entirely dependent on advection.
Indeed, there was essentially zero solute in the posterior ventricle at the
final simulation time (around 850 s), where transport is largely driven by diffusion.
For $D_1$, an estimate of the diffusion timescale $t_d=L^2/D_1$ over a distance
$L=200$ \textmu m from the middle to the posterior ventricle is approximately 24500 s.
Advective transport by the mean velocity $\overline{U}=1.41 \ \mu$m/s over the same distance would happen
on a timescale of the order of $t_a=L/\overline{U}=141$ s. Comparing this with the minuscule values of
$\cbar_6$ after simulating transport with $D_1$ for 850 s, one can conclude that if advection
played a role in transporting solute from the photoconversion site in the middle ventricle
to the posterior ventricle, values of $\cbar_6$ would be higher than those observed.

@@

\subsection*{Computational model assumptions and boundary conditions}
To model CSF, we employed slip boundary conditions at the ventricular walls,
contrasting the classical choice of a noslip boundary condition.
The use of slip boundary conditions is motivated by experimental observations of the
flow field in zebrafish embryo brain ventricles~\cite{Olstad2019CiliaryDevelopment}.
It has been observed, both previously and in this work, that the fluid velocity increases
towards the wall~(\Cref{fig:fig1}\fixme{c}).
Using slip boundary conditions allows for this behavior.
A couple of previous continuum model simulation studies of
cilia-mediated flow~\cite{Siyahhan2014FlowVentricles, Thouvenin2020OriginCanal}
have modeled cilia as body forces. We chose to model the cilia as a force exerted tangentially on the boundary.
First, we deem this a good representation of the real nature of cilia,
since they are in reality microscale structures confined to the ventricular walls that
generate flow through collective motion. Second, it avoids the need of excessive mesh
refinement near the ciliated boundaries in the case that a
body force were to be applied in a $\sim$ 5 \textmu m~\cite{Salman2022ComputationalEmbryo} deep cilia layer.

@@

Particle movement varied over the different measurements. The mean of $\overline{u}_x$ was
0.26 \textmu m/s and the mean of $\overline{u}_y$ was 0.08 \textmu m/s. The maximum mean velocities
in absolute values were 10.2 \textmu m/s and 2.4 \textmu m/s for $\overline{u}_x$ and $\overline{u}_y$,
respectively. We used the only-cardiac/no-cilia flow model to tune the pressure boundary condition
amplitude $A$. The choice of $A=0.0015$ Pa was used since: (i) it yields a maximum velocity magnitude
of 4.8 \textmu m/s, which is close to the maximum observed in the particle tracking data when
rejecting the outlier at around 10 \textmu m/s; (ii) it yields a time-averaged mean velocity
of 0.89 \textmu m/s, which is close to the mean observed in the particle tracking data.
\begin{figure}[H]
    \begin{minipage}[t]{0.49\textwidth}
        \includegraphics[width=\textwidth]{graphics/mean_velocities_x.png}
        \subcaption{Mean velocities in the $x$ direction of the particles tracked.}\label{fig:meanx}
    \end{minipage}
    \begin{minipage}[t]{0.49\textwidth}
        \includegraphics[width=\textwidth]{graphics/mean_velocities_y.png}
        \subcaption{Mean velocities in the $y$ direction of the particles tracked.}\label{fig:meany}
    \end{minipage} 
    \caption{Particle tracking data. The dashed horizontal line designates a value of zero.}\label{fig:particle_tracking_data}
\end{figure}
\clearpage
\bibliography{ref}{}
\end{document}
